Let $(X, d)$ be a metric space. Determine for each $A \subseteq X$ whether $A$ is open, closed, or neither in $X$.

a.  The set of integers $\mathbb{Z} \subset \mathbb{R}$ where $X = \mathbb{R}$ and $d$ is the usual metric.

\ \\
\emph{Claim.} $\mathbb{Z}$ is closed and not open.

\begin{proof}\renewcommand{\qedsymbol}{}\ \\\\
    Observe that $\mathbb{R} \setminus \mathbb{Z} = \bigcup\limits_{z \in \mathbb{Z}}{(z, z + 1)}$. Since each 
    $(z, z + 1)$ is open in $\mathbb{R}$ with respect to the usual metric, $\mathbb{R} \setminus \mathbb{Z}$ is the
    union of open sets and is therefore itself open. Since the complement of $\mathbb{Z}$ is open, $\mathbb{Z}$ itself
    is closed.

    Observe also that every open ball $B_\epsilon(1)$ centered about any $1 \in \mathbb{Z}$ contains a point in 
    $\mathbb{R} \setminus \mathbb{Q}$ by the density of the irrationals; hence there exists no open ball 
    $B_\epsilon(1) \subseteq \mathbb{Z}$, and so $\mathbb{Z}$ is not open.
    \ \\
\end{proof}

\pagebreak

b.  $A = \{(x, y) \in \mathbb{R}^2 \mid y=x^2, x \in \mathbb{Q} \}$ where $X = \mathbb{R}^2$ and $d$ is the Euclidean
     metric.

\ \\
\emph{Claim.} $A$ is neither closed nor open.

\begin{proof}\ \\\\
    Observe that the sequence of partial sums of the sequence $\{s_n\}$ defined by 
    $s_n = \sum\limits_{k = 0}^{n}{\frac{1}{k!}}$ is a sequence consisting of elements of $\mathbb{Q}$, but that
    $\{s_n\}$ converges to $e \in \mathbb{R} \setminus \mathbb{Q}$. Then the sequence $\{s_n, s_n^2\}$ is a sequence in
    of terms in $A$, and the element $(e, e^2)$ is a limit point\footnote{
        Since $f(x) = x^2$ is a continuous function in $(X, d)$, and $s_n$ converges to $e$, we have that 
        $f(s_n^2) = f(e^2)$.
    } of $A$ which is not in $A$. Hence $A$ is not closed.

    To show that $A$ is not open, observe that the point $(0, 0)$ lies in $A$, and consider any open ball $B_r((0, 0))$ 
    with $r > 0$ centered about $(0, 0)$. Then the point $(\frac{r}{2}, \frac{r}{2})$ is in the open ball, but is not in
    $A$; hence there exists no open ball centered about $(0, 0)$ which is entirely contained in $A$, and so $A$ is 
    not open.
    \ \\
\end{proof}

\pagebreak

c.  $A = \{(x, y, z) \in \mathbb{R}^3 \mid x^2 + y^2 + z^2 + 2z = 0 \}$, where $X = \mathbb{R}^3$ and $d$ is the 
    Euclidean metric.

\ \\
\emph{Claim.} $A$ is closed and not open.

\begin{proof}\ \\\\
    To show that $A$ is not open, consider the point $p = (0, 0, 0) \in A$, and observe that for any $\epsilon > 0$, the 
    open ball $B_\epsilon(p)$ centered about $p$ contains the point 
    $q = \left( \frac{\epsilon}{2}, \frac{\epsilon}{2}, \frac{\epsilon}{2} \right)$. Then because 
    $(\frac{\epsilon}{2})^2 + (\frac{\epsilon}{2})^2 + (\frac{\epsilon}{2})^2 + \epsilon > 0$, we have that $q$
    is not in $A$. Thus, there exists no open ball centered about $p \in A$ which is contained in $A$, and hence $A$ is
    not open.

    \ \\
    We next show that $A$ is closed by showing that $X \setminus A$ is open. Let  \linebreak
    $L = \{(x, y, z) \in \mathbb{R}^3 \mid x^2 + y^2 + z^2 + 2z < 0 \}$,
    $G = \{(x, y, z) \in \mathbb{R}^3 \mid x^2 + y^2 + z^2 + 2z > 0 \}$, and observe that $X \setminus A = L \cup G$.
    Moreover, observe that in the Euclidean metric, $L$ is precisely the open unit ball centered about the point 
    $r_0 = (0, 0, -1)$; since open balls are open sets, $L$ is therefore an open set.

    Let $p$ be a point in $G$, let $r = d(r_0, p) - 1$, and let $B_r(p)$ be the open ball of radius $r$ centered about
    $p$. \footnote{
        $r$ therefore represents the incremental distance between the edge of the unit sphere and the point $p$.
    }

    Consider an arbitrary point $q \in B_r(p)$, and observe that $d(r_0, q) \ge d(r_0, p) - d(p, q)$ by the Triangle
    Inequality. Furthermore, since $q$ is in $B_r(p)$, we have that $d(p, q) < r$, and so 
    $d(r_0, p) - d(p, q) > d(r_0, p) - r$. But $d(r_0, p) = 1 + r$, and so putting this all together yields the 
    following inequality:
    \begin{align*}
        d(r_0, q) &\ge d(r_0, p) - d(p, q) \\
                  &> d(r_0, p) - r \\
                  &> (1 + r) - r \\
                  &= 1.
    \end{align*}

    Hence $d(r_0, q) > 1$, and so $q \in G$. Since $q$ was chosen to be an arbitrary point in $G$, we have that 
    $B_r(p) \subseteq G$ is an open ball about $p$ which is entirely contained in $G$, and so $p$ is an interior point
    of $G$. Since $p$ was chosen to be an arbitrary point in $G$, every point of $G$ is an interior point, and so $G$
    must be open. Thus, $X \setminus A = L \cup G$ is the union of open sets and is therefore itself open, and so $A$
    is closed, as desired.
    \ \\
\end{proof}

\pagebreak

d.  $A = \{ f \in X \mid 0 < f(x) < 1, x \in [a, b] \}$ where $d(f, g) = \sup\limits_{x \in [a, b]}{|f(x) - g(x)|}$ and 
    $X = C[a, b]$.

\ \\
\emph{Claim.} $A$ is open and not closed. 

\begin{proof}\ \\\\
    We first show that $A$ is not closed. Observe that for every $n \in \mathbb{N}$, the function $f_n$ defined by 
    $f_n(x) = \frac{1}{n}$ defines a continuous function which takes values strictly between zero and one and so 
    $f_n \in A$ for all $n \in \mathbb{N}$. Moreover, for any $n \in \mathbb{N}$, we have the following:
    \begin{align*}
         d(f_n, 0) &= \sup\limits_{x \in [a, b]}{|f_n(x) - 0|} \\ 
                   &= \sup\limits_{x \in [a, b]}{|f_n(x)|} \\ 
                   &= \frac{1}{n}.
    \end{align*}

    Thus, for any fixed $\epsilon > 0$, we can find an $N \in \mathbb{N}$ such that $d(f_N, 0) < \epsilon$ and hence
    $f_N \in B_\epsilon(0)$. Since $f_N \neq 0$, we have that $g(x) = 0$ is a limit point of $A$ which is not in $A$, 
    and hence $A$ is not closed.

    \ \\
    We now show that $A$ is open. Let $g \in A$, and observe that because $g(x)$ is a continuous bounded function
    in $\mathbb{R}$ defined on a compact set $[a, b]$, $g(x)$ attains its maximum and minimum values on $[a, b]$. We 
    denote these values by $M$ and $m$, respectively, and observe that by definition of $A$, we have $0 < m \le M < 1$. 
    Let $\epsilon = \min{\{ d(g, 0), d(g, 1) \}} = \min{\{ m, 1 - M \}}$, and observe that $g(x) \ge m \ge \epsilon$ and 
    $1 - g(x) \ge 1 - M \ge \epsilon$ for all $x \in [a, b]$. Hence $g(x) - \epsilon \ge 0$ and $1 \ge g(x) + \epsilon$
    for all $x \in [a, b]$.

    With those inequalities in hand, we now consider the open ball $B_\epsilon(g)$ of
    radius $\epsilon$ centered about $g$. For any $h \in B_\epsilon(g)$, we have by definition that 
    $g(x) - \epsilon < h(x) < g(x) + \epsilon$ for all $x \in [a, b]$. By our earlier inequalities, we have that 
    $g(x) - \epsilon \ge 0$ and $g(x) + \epsilon \le 1$, and so $0 < h(x) < 1$ and therefore $h \in A$. Since $h$ was
    chosen to be an arbitrary element in $B_\epsilon(g)$, we have that $B_\epsilon(g) \subseteq A$, and so $g$ is an 
    interior point of $A$. Moreover, since $g$ was chosen to be an arbitrary element of $A$, we have that every point in
    $A$ is an interior point, and so $A$ is open.
    \ \\
\end{proof}

\pagebreak

e.  $A = \{ f \in X \mid \int_a^b{f(x) \,dx} = 0 \}$ where $d(f, g) = \sup\limits_{x \in [a, b]}{|f(x) - g(x)|}$ and 
    $X = C[a, b]$.

\ \\
\emph{Claim.} $A$ is closed and not open.

\begin{proof}\renewcommand{\qedsymbol}{}\ \\\\
    We first show that $A$ is not open. Observe that $X \setminus A = \{f \in X \mid \int_a^b{f(x) \,dx} \neq 0 \}$, and
    let $f_n$ be the constant function defined by $f_n(x) = \frac{1}{n(b - a)}$ for $n \in \mathbb{N}$. Then 
    $\int_a^b{f(x) \,dx} = \frac{1}{n} > 0$. As before, we have the following:


    \begin{align*}
         d(f_n, 0) &= \sup\limits_{x \in [a, b]}{|f_n(x) - 0|} \\ 
                   &= \sup\limits_{x \in [a, b]}{|f_n(x)|} \\ 
                   &= \frac{1}{n(b - a)}.
    \end{align*}

    Since $b - a > 0$ is constant, we may for any fixed $\epsilon > 0$ pick an $N \in \mathbb{N}$ to be large enough 
    (specifically, larger than $\frac{1}{\epsilon(b - a)}$) so that $d(f_N, 0) < \epsilon$. Hence $f_N$ is in
    the open ball $B_\epsilon(0)$ of radius $\epsilon$ centered about $g(x) = 0$. Since $\epsilon$ was chosen to be
    arbitrary, $g(x) = 0$ is a limit point of $X \setminus A$ which is not in $A$ (since $g(x) = 0$ integrates to zero 
    over any interval), and so $X \setminus A$ is not closed. Since $X \setminus A$ is not closed, $A$ is not open.

    TODO: Show that $A$ is not open.
\end{proof}

\pagebreak

f.  $A = \{ (x, y) \in X \mid y = f(x) \}$ where $X = \mathbb{R}^2$, $f:\mathbb{R} \to \mathbb{R}$ is continuous, and 
    $d$ is the Euclidean metric.

\ \\
\emph{Claim.} $A$ is closed and not open.

\begin{proof}\renewcommand{\qedsymbol}{}\ \\\\
    \begin{align*}
    \end{align*}
\end{proof}

\pagebreak