\textbf{Griva, Nash, Sofer 6.1.3}

Find the dual of 

\begin{maxi*}
  {}{z = 6x_1 - 3x_2 - 2x_3 + 5x_4}{}{}
  \addConstraint{4x_1 + 3x_2 - 8x_3 + 7x_4}{= 11}
  \addConstraint{3x_1 + 2x_2 + 7x_3 + 6x_4}{\ge 23}
  \addConstraint{7x_1 + 4x_2 + 3x_3 + 2x_4}{\le 12}
  \addConstraint{x_1, x_2 \ge 0,\; x_3 \le 0, \,}{x_4 \; \text{unrestricted}}
\end{maxi*}

and verify that the dual of the dual is the primal.

\begin{solution}
  Since the primal problem is a maximization problem, the dual is a minimization problem. The first constraint in the 
  primal is an equality constraint, and so $y_1$ in the dual is unrestricted. The second constraint is reversed with 
  respect to the canonical form of maximization problems, and so $y_2$ must be nonpositive. The third constraint is 
  consistent with canonical form, and hence $y_3$ is nonnegative.

  The variables $x_1$ and $x_2$ in the primal are consistent with canonical form, and so the first two constraints in
  dual must also be consistent with canonical form for the dual minimization problem. The third variable $x_3$ is 
  nonpositive and so the third constraint in the dual must be reversed. The fourth variable $x_4$ is unrestricted which
  yields an equality constraint for the final constraint in the dual.

  The dual of this program is therefore given by:

  \begin{mini*}
    {}{w = b^T y = 11y_1 + 23y_2 + 12y_3}{}{}
    \addConstraint{A_1^T y =  4y_1 + 3y_2 + 7y_3}{\ge 6 = c_1}
    \addConstraint{A_2^T y =  3y_1 + 2y_2 + 4y_3}{\ge -3 = c_2}
    \addConstraint{A_3^T y = -8y_1 + 7y_2 + 3y_3}{\le -2 = c_3}
    \addConstraint{A_4^T y =  7y_1 + 6y_2 + 2y_3}{= 5 = c_4}
    \addConstraint{y_1 \; \text{unrestricted}, \; y_2 \le 0, \;}{y_3 \ge 0}.
  \end{mini*}
  \ \\

  Because the dual is a minimization problem, the dual of the dual is a maximization problem. Since $y_1$ is 
  unrestricted, the first constraint in the dual of the dual is an equality constraint. The second variable $y_2$ in the
  dual is nonpositive, and so the second constraint in the dual of the dual is reversed from canonical form. The third 
  variable $y_3$ in the dual is nonnegative, and hence the final constraint in the dual of the dual is consistent with
  canonical form.

  The first two constraints of the dual are consistent with canonical form, and so the first two variables $x'_1$ and 
  $x'_2$ in the dual of the dual are nonnegative. Conversely, the third constraint of the dual is opposite canonical
  and so $x'_3$ in the dual of the dual is nonpositive. Since the fourth constraint in the dual is an equality 
  constraint, $x'_4$ is unrestricted. Putting this all together, taking the transpose of the coefficients, and swapping
  the roles of $b$ and $c$ yields:

  \begin{maxi*}
    {}{z = 6x'_1 - 3x'_2 - 2x'_3 + 5x'_4}{}{}
    \addConstraint{4x'_1 + 3x'_2 - 8x'_3 + 7x'_4}{= 11}
    \addConstraint{3x'_1 + 2x'_2 + 7x'_3 + 6x'_4}{\ge 23}
    \addConstraint{7x'_1 + 4x'_2 + 3x'_3 + 2x'_4}{\le 12}
    \addConstraint{x'_1, x'_2 \ge 0,\; x_3 \le 0, \,}{x'_4 \; \text{unrestricted}}
  \end{maxi*}

  which is precisely the primal problem.
  \ \\
\end{solution}
