\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[bottom]{footmisc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{upref}
\usepackage[hidelinks]{hyperref}
\usepackage{cite}
\usepackage{subcaption}
\usepackage{xfrac}
\usepackage{bm}
\usepackage{mathtools}
\usepackage{ifthen}
\usepackage{optidef}

\setlength{\textwidth}{6.4in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-1in}
\addtolength{\headheight}{0.0675in}
\setlength{\oddsidemargin}{0.2in}
\setlength{\evensidemargin}{0.2in}

\let\oldcite=\cite
\renewcommand\cite[1]{\ifthenelse{\equal{#1}{NEEDED}}{[citation~needed]}{\oldcite{#1}}}

\begin{document}

    \title{%
        1D Shallow-Water Wave Equation with Inferred Bathymetry\\
        \large A Physics-Informed Neural Network Approach
    }
    \author{%
        Nameika, Michael \\
        Thompson, Jonathan
    }
    \date{\today}
    \maketitle

    \begin{abstract}
        In this project, we examine a Physics-Informed Neural Network (PINN) approach to solving a 1D system of 
        shallow-water equations with variable bathymetry. We begin by stating the system of equations with variable
        bathymetry and from there derive the system of equations corresponding to a constant bathymetry with negligible
        frictional forces. From there, we solve the resulting system via pseudospectral methods for various boundary
        and initial conditions. We then use the results of this computation as sampled data with which to train a 
        Physics-Informed Neural Network (PINN); in this scheme, we treat the bathymetry as an unknown and allow the 
        neural network to infer the solution and bathymetry simultaneously. Lastly, we compare the results of the PINN
        approach to the results of the pseudospectral approach and discuss the advantages and disadvantages of each.
    \end{abstract}

    \section{Background}\label{sec:background}

    \input{background.tex}

    \section{Methodology}\label{sec:proposed-methodology}

    \subsection{Method of Characteristics}\label{subset:moc-methodology}

    \input{moc.tex}

    \subsection{Pseudospectral Methods}\label{subsec:pseudospectral-methodology}

    \input{pseudospectral.tex}

    \subsection{Physics-Informed Neural Networks}\label{subsec:pinn-methodology}

    \input{pinn.tex}

    \section{Comparison}\label{sec:comparison}
    
    \section{Conclusions and Future Work}\label{sec:conclusion}

    The following is a list of possible future directions for this work:

    \begin{enumerate}
        \item Allow the bathymetry to vary in space and solve the resulting system via Discontinuous Galerkin methods.
        \item Introduce frictional forces into the system and solve the resulting system via pseudospectral methods. In
              this paradigm, the friction coefficient will be treated as a parameter to be learned by the neural 
              network.
        \item Extend this problem to the two-dimensional case.
    \end{enumerate}

    \pagebreak

    \bibliographystyle{plain}
    \bibliography{refs}

    \pagebreak
    \appendix
    \input{appendix_a.tex}

\end{document}
