Prove that the union of a finite collection of finite sets is finite. 

\begin{proof}\ \\\\

    Let $\mathcal{S}$ denote a finite collection of finite sets. If $\mathcal{S}$ is empty, the union of all sets in
    $\mathcal{S}$ is empty, and is therefore by definition finite. Furthermore, if $\mathcal{S}$ consists
    of a single finite set, the union of all sets in $\mathcal{S}$ is simply the single finite set which comprises 
    $\mathcal{S}$ and is therefore finite.

    To show that unions of finite collections of finite sets are finite, we proceed by induction on
    the number of elements in the collection, which we denote $n$.

    We begin by establishing our base case for $n = 2$, and let $S_1$ and $S_2$ be finite sets.
    If both sets are empty, then $S_1 \cup S_2 = \emptyset$, which is finite. If $S_1$ is empty,
    then $S_2 \cup S_1 = S_2$ and hence $S_2 \cup S_1$ is finite; a similar
    argument holds if $S_2$ is empty.

    We may therefore assume that $S_1$ and $S_2$ are non-empty. Because $S_1$
    and $S_2$ are finite, there exist bijections $\phi_1:S_1 \to \{k\}_{k=1}^n$
    and $\phi_2:S_2 \to \{k\}_{k=1}^m$ for some $n, m \in \mathbb{N}$. We construct a 
    bijection $\phi:(S_1 \cup S_2) \to \{k\}_{k=1}^N, N \le m+n$
    defined by:
    
    \begin{align*}
        \phi(s) = \begin{cases}
            \phi_1(s), s \in S_1 \\
            \phi_2(s), s \in S_2 \backslash S_1 \\
        \end{cases}
    \end{align*}

    Observe that $\phi$ carries elements uniquely from $S_1 \cup S_2$ to $\{k\}_{k=1}^N$ and
    that because $S_1 \cup S_2 = S_2 \cup (S_1 \backslash S_2)$, every element of $S_1 \cup S_2$ 
    maps to a value in $\mathbb{N}$. Hence $\phi$ is bijective and since we have shown
    the existence of a bijection from $S_1 \cup S_2$ to a set $\{k\}_{k=1}^N$, the set $S_1 \cup S_2$ is finite
    and our base case is established. 

    Now suppose that the union $\bigcup\limits_{i=1}^{n}{S_i}$ of a collection of finite sets $\{S_i\}_{i=1}^{n}$ 
    is finite for $n \in \mathbb{N}$ sets, and let $\bigcup\limits_{i=1}^{n+1}{T_i}$ represent the union of a collection
    of $n+1$ arbitrary finite sets. Then
    $\bigcup\limits_{i=1}^{n+1}{T_i} = \bigcup\limits_{i=1}^{n}{T_i} \cup \{T_{n+1}\}$.  Observe that $T_{n+1}$ is a
    finite set by assumption and that $\bigcup\limits_{i=1}^{n+1}{T_i}$ is finite by our
    inductive hypothesis; hence $\bigcup\limits_{i=1}^{n}{T_i} \cup \{T_{n+1}\}$ is nothing more than the union of two
    finite sets and is therefore itself finite by our base case. By the Principal of Mathematical Induction,
    the union of a finite collection of finite sets is therefore finite.

\end{proof}